\documentclass{stint-cv}
\newcommand{\cvToday}{20 July 2018}

\begin{document}
\changefont{pbk}
\cvMakeHeaderFooter{2-Page CV}{Gy\"orgy D\'an, PhD}
\pagenumbering{arabic}

%\cvPersonalInfoLogo
\cvPersonalInfoLogo{kth-logo}
{Gy\"orgy D\'an}
{Professor}
{Department of Computer Science, Karlstad University, Sweden}
{+46 722 80 20 67}{+46 54 700 2429}{javid.taheri@kau.se}
{https://sites.google.com/site/javidtaheri75/home}
{https://scholar.google.co.uk/citations?user=QTNsnbAAAAAJ}


\cvHeadingTwoPageCV{Academic Positions}
\begin{cvItemize}
	\cvDatedItem{Associate Professor: Department of Computer Science, Karlstad University, Sweden.}{2015--present}
	\cvDatedItem{Research Fellow: School of Information Technologies, University of Sydney, Australia.}{2007--2015}
	\cvDatedItem{Part-time Lecturer, School of Information Technologies, University of Sydney, Australia.}{2007--2015}
	\cvDatedItem{Adjunct Lecturer: School of Computing and Mathematics, Charles Sturt University, Australia.}{2013--2017}
\end{cvItemize}

\cvHeadingTwoPageCV{Education}
\begin{cvItemize}
	\cvDatedItem{Ph.D. of Information Technologies, School of Information Technologies, University of Sydney, Australia.}{2003--2007} 
	\cvDatedItem{Graduate Certificate in Educational Studies (Higher Education), University of Sydney, Australia.}{2013-2014}
	\cvDatedItem{M.Sc. of Electrical Engineering, Sharif University of Technology, Tehran, Iran.}{1998--2000}
	\cvDatedItem{B.Sc. of Electrical Engineering, Sharif University of Technology, Tehran, Iran.}{1993--1998}
\end{cvItemize}


\cvHeadingTwoPageCV{Honours}
\begin{cvItemize}
	\cvDatedItem{Wilkes Award from OXFORD ACADEMIC: The Computer Journal}{2018}
	\cvLongDatedItem{Selected as one of the top 200 young researchers in the world in Mathematics and Computer Science by the}{Heidelberg Laureate Forum, Germany.}{2013} 
	\cvLongDatedItem{Recipient of International Postgraduate Research Scholarship (IPRS) from the Australian Department of}{Education and Training.}{2003}
	\cvDatedItem{Recipient of the Full Stipend PhD Scholarship from University of Sydney.}{2003}
	\cvDatedItem{Recipient of the Top-up scholarship from the School of Information Technologies, University of Sydney.}{2003}
	\cvDatedItem{Ranked 9th among $\approx$10,000 in Iranian national university entrance exam for the M.Sc. program.}{1998}
	\cvDatedItem{Ranked 12th among $\approx$100,000 in Iranian national university entrance exam for the B.Sc. program.}{1993}
\end{cvItemize}

\cvHeadingTwoPageCV{Research Experience}
\begin{cvItemize}
	\cvDatedItem{Associate Professor \& Docent, Research in Cloud Computing, KaU, Sweden.}{2015--present}
	\cvDatedItem{Research Fellow in Clouds Computing, University of Sydney, Australia.}{2012--2015}
	\cvDatedItem{Research Fellow in Grid/Cloud Computing, University of Sydney, Australia.}{2009--2012}
	\cvDatedItem{Research Fellow in Networking, National ICT of Australia.}{2008-2009}
	\cvDatedItem{Postdoctoral Research in Bioinformatics, University of Sydney, Australia.}{2006--2008}
\end{cvItemize}

\cvHeadingTwoPageCV{Teaching Experience}
\begin{cvItemize}
	\cvDatedItem{Lecturing at Department of Computer Science, Karlstad University, Sweden.}{2015--present}
	\cvDatedItem{Lecturing at School of Information Technologies, University of Sydney, Australia.}{2008--2013}
	\cvDatedItem{Tutoring at School of Information Technologies, University of Sydney Australia.}{2004--2005}
	\cvDatedItem{Tutoring at different universities, Iran and Australia.}{1998--2004}
\end{cvItemize}


\cvHeadingTwoPageCV{Funds and Grants {\cvFontLarge (\underline{five} omitted due to page limitation)}}
\begin{cvItemize}
	\cvGrantItem{WISR17: Web-based Courses for International Positioning of Strategic Research Groups}
	{Work Package Collaborator, KK-stiftelsen(KKS)-NU17, 6.38m SEK $\approx$ \euro{638k} (5.7m SEK $\approx$ \euro{570k} funded by KKS)}
	{3Y: 2018--2020}
	
	\cvGrantItem{HITS: High Quality Networked Services in a Mobile World}
	{Work Package Leader since 2017, KK-stiftelsen(KKS)-Profile, 76m SEK $\approx$ \euro{7.6m} (36m SEK $\approx$ \euro{3.6m} funded by KKS)}
	{6Y: 2014--2020}
	
	
	\cvGrantItem{MACoMEC: Collaborative Mobility-Aware Computation Offloading for Mobile Edge Computing}
	{Principal Investigator, STINT Initiation Grant, 726k SEK $\approx$ \euro{75k} (150k SEK $\approx$ \euro{16k} funded by STINT)}
	{1Y:2017-2018}
	
	\cvLongGrantItem{NFV-Optimizer: Profiling Network Virtualized Functions and Optimizing their Performance}{for Telecom Clouds.}
	{Principal Investigator, KK-stiftelsen(KKS)--H{\"O}G,14.05m SEK $\approx$ \euro{1.4m} (4.75m SEK $\approx$ \euro{481k} funded by KKS)} {3Y:2017--2019}
	
	\cvGrantItem{Contention-Aware Scheduling in Cloud Data Centres}
	{Principal Investigator, Australian Research Council (ARC): Industry Linkage Grant, A\$574.9k $\approx$ \euro{400k}}
	{3Y:2016--2018}

%	\cvGrantItem{Updating Cloud Platform for School of Information Technologies}
%	{Principal Investigator, University of Sydney: Major Equipment Scheme, A\$65k $\approx$ \euro{45k}}
%	{1Y:2015}

%	\cvLongGrantItem{Optimising Service Level Agreements for Performance and Energy Efficiency in Cloud}{Computing Systems}
%	{Work Package Collaborator, Australian Research Council (ARC): Discovery Grant, A\$366k $\approx$ \euro{259k}}
%	{3Y:2013--2015}

%	\cvGrantItem{Build a Cloud Platform for the School of Information Technologies}
%	{Principal Investigator, University of Sydney: Major Equipment Scheme, A\$60k $\approx$ \euro{41.7k}}
%	{1Y:2013}

	\cvGrantItem{Holistic Energy-Aware Scheduling for Distributed Computing Systems}
	{Work Package Leader, Australian Research Council (ARC): Discovery Grant, A\$930k $\approx$ \euro{657k}}
	{5Y:2010--2014}
	
	\cvGrantItem{Replica Placement in Data-intensive Distributed Computing Systems}
	{Work Package Leader, Australian Research Council (ARC): Discovery Grant, A\$250k $\approx$ \euro{176k}}
	{3Y:2010--2012}
	
%	\cvGrantItem{Data and Job Scheduling in Large-Scale Distributed System}
%	{Work Package Leader, Australian Research Council (ARC): Discovery Grant, A\$443k $\approx$ \euro{313k}}
%	{3Y:2008--2010}

%	\cvGrantItem{Parallel Algorithms for Mobility Management}
%	{Work Package Leader, University of Sydney Deputy Vice-Chancellor: Research/Bridging Support, A\$15k $\approx$ \euro{10.6k}}
%	{1Y:2008}
	
	\cvGrantItem{Protein Secondary Structure Prediction}
	{Principal Investigator, University of Sydney Deputy Vice-Chancellor: Early Career Research Scheme, A\$40k $\approx$ \euro{27.8k}} {1 1Y:2008}
\end{cvItemize}


\cvHeadingTwoPageCV{Professional Leadership and Editorships}
\begin{cvItemize}
	\cvDatedItem{Examiner/reviewer for various grant and funding agencies (Australia, Sweden, Canada, etc.)}{Since 2015 }
	\cvDatedItem{Conference organising committee/chair of 19 respected Conferences (P2Mnet, CloudCom, ISPA, etc.)}{Since 2013}
	\cvDatedItem{Journal/book guest/associate editor (IET, John Wiley \& Sons, Hindawi, etc.)}{Since 2010}
	\cvDatedItem{Examiner for postgraduate theses (USyd, KTH, Lund, Ume\aa, TUW, etc.)}{Since 2008}
	\cvDatedItem{Journal Reviewer for >40 respected Journals (IEEE, Elsevier, John Wiley, Springer, etc.)}{Since 2007}
	\cvDatedItem{Conference technical program committee of >60 conferences (IEEE NFV-SDN, iThings, GlobeCom, etc.)}{Since 2006}
\end{cvItemize}

\cvHeadingTwoPageCV{Research and Teaching Interests}
\begin{cvItemize}
	\cvItem{Edge/Fog/Cloud Computing}
	\cvItem{Parallel/Distributed Computing}
	\cvItem{Networking}
	\cvItem{Artificial Intelligence}
	\cvItem{Algorithms}
\end{cvItemize}

\cvHeadingTwoPageCV{Publications}
\bigbreak
\begin{center}
	\vspace{-1.5em}
	\newcommand\tstrut{\rule{10pt}{2.4ex}}
	\newcommand\bstrut{\rule[-10.0ex]{10pt}{10pt}}
\begin{tabular}{c C{1cm} c}
\begin{tabular}{l c r r}
	&& Total & Since 2013\\
	\arrayrulecolor{gray}\hline \\[-1.0em]
	Edited book &:& 1 & 1 \\
	Book chapters &:& 20 & 10 \\
	Journal articles &:& 39 & 24  \\
	Conference papers &:& 66 & 17 \\
	Technical reports &:& 9 & 0
\end{tabular}
&&
\begin{tabular}{l c r r}
	&& Total & Since 2013\\
	\arrayrulecolor{gray}\hline \\[-1.0em]
	Citation count 	&:& 1596 & 1219\\
	h-index 		&:& 21 	& 18\\
	i10-index 		&:& 46 	& 37 \\
	\tabularnewline
	\tabularnewline
\end{tabular}
\end{tabular}
\end{center}

\cvHeadingTwoPageCV{Pedagogical/Industrial Certificates}
\begin{cvItemize}
	\cvDatedItem{VCP5-DCV: VMware Certified Professional 5 -- Data Center Virtualization.}{2014}
	\cvDatedItem{VCP5-DT: VMware Certified Professional 5 -- Desktop.}{2014}
	\cvDatedItem{VCP5-Cloud: VMware Certified Professional 5 -- Cloud.}{2014}
	\cvDatedItem{Microsoft Azure for Research Training.}{2014}
	\cvDatedItem{CCNA: Cisco Certified Network Associate.}{2013}
	\cvDatedItem{Principles and Practice of University Teaching and Learning, University of Sydney.}{2013}
	\cvDatedItem{Foundations of Research Supervision, University of Sydney.}{2013}
	\cvDatedItem{IBM Certified Academic Associate: DB2 Academic Training.}{2012}
\end{cvItemize}

\cvHeadingTwoPageCV{Student Supervision (PhD/Masters/Honors)}
\begin{cvItemize}
	\cvItem{Graduated students: 8 PhDs, 5 Masters/Honours, 4 Bachelors}
	\cvItem{Current students: 6 PhDs}
\end{cvItemize}

\cvHeadingTwoPageCV{Selected Publications}
\nobibliography{javid-publication-cv}
\bibliographystyle{ieeetr}
\begin{enumerate}[label={[\arabic*]}]	
	\itemsep=-0.3em
	\itemindent=-0.3em 
	\small
	\item \bibentry{J-39}
	\item \bibentry{J-33}
	\item \bibentry{J-32}
	\item \bibentry{J-35}
	\item \bibentry{J-31}
\end{enumerate}

\end{document}
